---
title: "Embedding Plotly Plots into Substack"
output: html_document
date: "2026-02-20"
---


Export Your Plotly Plot as a HTML Widget

```{r}
#install.packages("htmlwidgets)
library(htmlwidgets)
#install.packages("plotly")
library(plotly)
library(ggplot2)
```


Create Plot and Convert to Plotly Plot

```{r}

example_df = data.frame(
  "state" = c("CT","RI","NY","MA","PA","ME"),
  "value" = c(1,2,3,4,5,6))

example_plot = ggplot(data = example_df, aes(x = state, y = value, color = state), ) +
  geom_point()
example_plot


example_plotly = plotly::ggplotly(example_plot, tooltip = c("y", "x"))
example_plotly

```

Save Plotly as HTML to Working Directory

```{r}

setwd("C:/Users/asare/Downloads")
saveWidget(as_widget(example_plotly), "example_plotly.html", selfcontained = TRUE)
```



Embed Plotly HTML in Substack

1. Upload the HTML file into the PopHIVE Github Substack Repository folder that is relevant to your blog post
2. Insert Github Pages link to your Plotly HTML website into your blog post. YOU MUST USE THE FOLLOWING LINK https://pophive.github.io/Substack/INSERT THE PATH TO YOUR PLOTLY HTML FILE.html

  - In this example: https://pophive.github.io/Substack/Plotly - Substack Demo/example_plotly.html --> Insert this link into your blog post

